POMDP comparisons across sigma_m, sigma_g

### 2017-10-11 appendix/appendixB.Rmd
tidy up appendixB
ensure alignment on scenarios

@@

- Currently parameter estimates are just MLE. Should do Bayesian version (slower of course, and tricky to summarize; maybe just as sds around estimates.)

@@

Do the estimates make sense?

@@

```{r}
pars <- fits %>% ungroup() %>% select(commonname, r, K, sigma_g) 
```

```{r}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(sarsop)       # the main POMDP package
library(tidyverse)    # for munging and plotting
library(parallel)
options(mc.cores = 4) # Reserve ~ 10 GB per core
log_dir <- "pomdp_historical"
```

@@

## POMDP solution (slow, >20,000 seconds per loop memory intensive)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = meta[i, "r"][[1]], 
                             K = meta[i, "K"][[1]], 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal",
                             commonname = meta[i, "commonname"][[1]])

@@

```{r}
meta <- meta_from_log(data.frame(model="gs"), log_dir) %>%
  mutate(scenario  = as.character(1:length(sigma_m)))
alphas <- alphas_from_log(meta, log_dir)
#models <- models_from_log(meta)
```

>>>>

# Section 1: Model estimates from data

@@

@@

<!--
Do the estimates make sense?  Consider simulation from models, under this historical harvests, compared to historical trajectories

@@

-->

```{r}
pars <- fits %>% ungroup() %>% select(commonname, r, K, sigma_g) 
pars
```

-------

# Decision Policies

```{r}
options(mc.cores = 4) # Reserve ~ 10 GB per core
log_dir <- "pomdp_historical"
```

@@

## POMDP solution (slow, >20,000 seconds per loop memory intensive)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = meta[i, "r"][[1]], 
                             K = meta[i, "K"][[1]], 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal",
                             commonname = meta[i, "commonname"][[1]],
                             scenario = meta[i, "scenario"][[1]])

@@

```{r}
meta <- meta_from_log(data.frame(model="gs"), log_dir)  %>% 
  left_join(
    select(meta, sigma_m, commonname, scenario), 
    by = c("sigma_m", "commonname")) %>% 
  arrange(scenario)
alphas <- alphas_from_log(meta, log_dir)
#models <- models_from_log(meta)
```
